Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-02 02_Paper/paper.tex

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Koke}
\author[a]{Fabian Steinberg} 
\author[a]{Alejandro R. Pérez M.}
\author[b,c]{Jochen Garcke}
\author[b]{Daniela Steffes-Lai}
\author[b,d]{Moritz Wolter}

@@

\section{Related Works} % 1 Page

@@

% b)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page

@@

% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]

\section{Experiments} % 1.5 Pages

>>>>

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Koke}
\author[a]{Fabian Steinberg} 
\author[a]{Alejandro R. Pérez M.}
\author[a]{Lennart Schmallenbach}
\author[b,c]{Jochen Garcke}
\author[b]{Daniela Steffes-Lai}
\author[b,d]{Moritz Wolter}

@@

\section{Related Works} % 1 Page \Lennart

@@

% Predictive analytics as concepts
% Implementation in production
%   - Predictive Maintenance
%   - Scheduling
%   - Other

% If happens to be something with P.A. Quality Check
% b)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

% Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases

@@

% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]
\subsection{Measurement}

\subsection{Machine Learning}

\section{Experiments}

\subsection{Recording the data}

\subsection{Classifier optimization and testing}

\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
\end{table}

\section{Conclusion}
